%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {R\&D Lead Engineer, Flamapp.ai} % Role
    {Talking Avatar} % Project
    {Bengaluru} % Location
    {Jan 2026 - Present} % Date(s)
    {
      \begin{cvitems}
        \item Led development of a real-time talking avatar system generating photorealistic video from a single image/video conditioned on audio.
  \item Achieved <1.2s time-to-first-frame (TTFF) on two RTX 4090, with scalable 1080p–4K output.
  \item Designed a distributed inference pipeline with multi-model batching, improving throughput and cost efficiency.
  \item Reduced video generation cost to <\$0.26/min, competitive with state-of-the-art commercial systems.
  \item Developed a novel multi-model architecture, contributing to the company's IP portfolio.
  \item Achieved ~78\% fool rate in human evaluation (n=24), indicating strong perceptual realism.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {R\&D Lead Engineer, Flamapp.ai} % Role
    {3D Reconstruction via Non-Markovian Process} % Project
    {Bengaluru} % Location
    {Apr 2025 - Aug 2025} % Date(s)
    {
      \begin{cvitems}
        \item Led development of a 3D reconstruction system generating textured meshes from multi-view images/videos.
        \item Designed a differentiable rendering pipeline enabling end-to-end optimization, reducing reliance on traditional bundle adjustment for faster camera parameter estimation.
        \item Developed a single-shot architecture for joint geometry and texture generation in a single forward pass.
        \item Leveraged a pretrained VAE with a custom loss function to improve texture fidelity and fine detail reconstruction.
        \item Generated high-quality triangle meshes via Marching Cubes with accurate texture projection.
        \item Achieved ~0.3 px reprojection error at 25 cm and >95\% text recovery rate for characters >0.3 cm.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {R\&D Lead Engineer, Flamapp.ai} % Role
    {Differentiable Keypoint Extraction (Patent Filed) and ICP-based Image/3D Object Tracking} % Project
    {Bengaluru} % Location
    {Aug 2023 - Dec 2024} % Date(s)
    {
      \begin{cvitems}
        \item Led development of a production-grade SDK for real-time 6-DoF object pose estimation on embedded devices, given a reference 3D model.
        \item Designed a differentiable, trainable keypoint extraction algorithm outperforming ORB, SIFT, and BRISK in robustness and efficiency.
        \item Enabled reliable pose estimation for both rigid and planar objects using learned keypoints and geometric alignment.
        \item Integrated an ICP-based refinement pipeline for accurate pose recovery under real-world conditions.
        \item Optimized for edge deployment with size less than 260KB, resulted in SDK integration in production systems and commercial contracts.
        \item Resulted in a patented approach deployed in one of the company’s core products.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {R\&D Engineer, Flamapp.ai} % Role
    {Hyper-Personalized Augmented Objects (Published Patent)} % Project
    {Bengaluru} % Location
    {Jan 2022 - Dec 2022} % Date(s)
    {
      \begin{cvitems}
        \item Developed an object retrieval system for large-scale databases, enabling accurate matching when the query object occupies a small region of the input image.
        \item Designed an embedding-based similarity pipeline using a modified DeiT architecture for robust feature extraction under clutter and partial visibility.
        \item Improved retrieval performance for visually similar objects through enhanced representation learning and matching strategies like contrastive learning and triplet loss.
        \item Contributed to a patented system (US20250014287A1) integrated into the company’s core product.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {R\&D Engineer, Flamapp.ai} % Role
    {Method and System for Improvised Human Motion} % Project
    {Bengaluru} % Location
    {Jan 2023 - May 2023} % Date(s)
    {
      \begin{cvitems}
        \item Improved monocular human motion tracking using an RNN-based iterative correction framework under natural motion constraints.
        \item Collected and utilized motion capture (MoCap, Rokoko) data to train and refine temporal motion models.
        \item Enhanced motion realism and temporal consistency in reconstructed human poses.
        \item Contributed to a patented system (WO2024189648A1) integrated into the company’s core product with industry veterans from Microsoft , ex VP of engineering of the company and researchers from IIIT-H.
        \item Achived Joint Quaternion cosine distance loss of 0.05(Increasing in FK chains) for the joint angles and 0.01 for the root position with a total loss of 0.06 .
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
